---
title: "Exploratory"
author: "Emma Vestesson"
date: "02/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(THFstyle)
library(lubridate)
```

## Load data

```{r}
THF_red <- '#dd0031'
all_deaths <- readRDS( here::here('data', 'home_care_table_9.rds'))
covid_deaths <- readRDS( here::here('data', 'home_care_table_8.rds'))
home_care <- readRDS( here::here('data', 'home_care.rds'))
```


When you plot number of deaths without any aggregation or adjustment you get a lot of variation as the data is by date reported to CQC and there is a drop in reporting at the weekend. 

```{r}
ggplot(all_deaths, aes(x=date, y=home_care_service_user)) +
  geom_line(colour=THF_red) + 
  scale_x_date(date_breaks = '3 month') +
  theme_THF() + 
  labs(x='', y='', 
       title = 'Number of deaths by day reported to CQC')
```

Attempt to plot number of deaths summarised by week to reduce the variation. 


```{r}
all_deaths_weekly <-all_deaths %>% 
  mutate(date=floor_date(date, unit = "week", week_start = 1)) %>% 
  group_by(date) %>% 
  summarise_all(sum)

covid_deaths_weekly <-covid_deaths %>% 
  mutate(date=floor_date(date, unit = "week", week_start = 1)) %>% 
  group_by(date) %>% 
  summarise_all(sum)

ggplot(all_deaths_weekly, aes(x=date, y=home_care_service_user)) +
  geom_line(colour=THF_red) + 
  scale_x_date(date_breaks = '3 month') +
  theme_THF() + 
  labs(x='', y='', title = 'Number of deaths by week reported to CQC')
  
```
Weeekly bar plot

```{r}
ggplot(all_deaths_weekly, aes(x=date, y=home_care_service_user)) +
  geom_col(fill=THF_red) + 
  scale_x_date(date_breaks = '3 month') +
  theme_THF() + 
  labs(x='', y='', title = 'Number of deaths by week reported to CQC')
```

Where are people receiving home care dying? total 
```{r}
covid_deaths_weekly %>% 
  pivot_longer(-date, names_to = 'location') %>% 
  group_by(location) %>% 
  summarise(value=sum(value)) %>% 
  ggplot(.,aes(y=value, x=location)) + geom_col(fill=THF_red) +
 scale_fill_THF() + labs(x='', y='', title='Place of death') +
  theme_THF()

ggsave(here::here('output', 'place_of_death_home_care_service_user_bar_chart.png'))
```


Where are people receiving home care dying? Over time
```{r}
covid_deaths_weekly %>% 
  pivot_longer(-date, names_to = 'location') %>% 
  ggplot(.,aes(x=date, y=value, colour=location)) + geom_line() + 
  geom_point(size=2) + geom_point(colour='white') +
    scale_x_date(date_breaks = '1 week') + scale_colour_THF() +
  theme_THF()
ggsave(here::here('output', 'place_of_death_home_care_service_user_line_chart.png'))
```


add COVID-19 bars
```{r}
home_care %>% 
  filter(date>'2019-04-01') %>% 
mutate(date=floor_date(date, unit = "week", week_start = 1)) %>% 
  dplyr::group_by(date, type) %>% 
  dplyr::summarise(value=sum(value)) %>% 
   ggplot(.,aes( x=date)) + geom_col(aes(y=value, fill=type)) +
  scale_fill_THF() + labs(x='', y='', title='Place of death') +
  theme_THF()

ggsave(here::here('output', 'place_of_death_home_care_service_user_line_chart.png'))
```


